Final_Project_Work_HW2_JaJuArEm

### 2022-09-29 Final_Project_Work_HW2.Rmd
Fixed model, making it more simple for now

```{r}
full_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
    #step_rm(Series_Title, Released_Year, Overview) %>% variables causing issues, maybe this will work
    step_nzv(all_predictors()) %>% 
    step_normalize(all_numeric_predictors()) %>% 
    step_dummy(all_nominal_predictors())

>>>>

```{r}
full_rec <- recipe(Gross ~ ., data = imdb_clean) %>%
    step_rm(Series_Title, Released_Year, Overview,
            Director, Star1, Star2, Star3, Star4, Genre_2, Genre_3) %>% #variables causing issues
    step_nzv(all_predictors()) %>% 
    step_normalize(all_numeric_predictors()) %>% 
    step_dummy(all_nominal_predictors())
